Manuscript Assignment = Calcasieu

### 2025-04-18 Manuscript_Assignment.qmd
c

@@

```{r - abundance}
#| echo: TRUE

>>>>

Overlap
```{r yearly comparisons - plot}
#| echo: FALSE
d = df_ov |> 
  filter(ychange == 1)

# overlap
ggplot(d, aes(y2, sorensen,color="blue"))+
  geom_point(size = 2)+
  geom_line(linewidth = 1)+
  labs(x = 'Year', y = 'Overlap')+
  scale_fill_viridis_d(option = 'turbo')+
  scale_color_viridis_d(option = 'turbo')+
  theme_bw()+
  #facet_wrap(~BASIN, nrow = 2)+
  theme(axis.title = element_text(size = 14), 
        axis.text = element_text(size = 14, colour = "gray0"), 
        plot.title = element_text(size = 14, hjust=0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = 'none',
        legend.title = element_text(size = 14),
        strip.text.x = element_text(size = 14),
        legend.text = element_text(size = 12))

Centroid Distance
```{r yearly comparisons - plot2}
#| echo: FALSE

# centroid distance 
ggplot(d, aes(y2, dist_cent))+
  geom_hline(aes(yintercept = 1), linetype = 'dashed', linewidth = 1)+
  geom_point(size = 2)+
  geom_line(linewidth = 1)+
  labs(x = 'Year', y = 'Centroid distance')+
  scale_fill_viridis_d(option = 'turbo')+
  scale_color_viridis_d(option = 'turbo')+
  theme_bw()+
  #facet_wrap(~BASIN, nrow = 2)+
  theme(axis.title = element_text(size = 14), 
        axis.text = element_text(size = 14, colour = "gray0"), 
        plot.title = element_text(size = 14, hjust=0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = 'none',
        legend.title = element_text(size = 14),
        strip.text.x = element_text(size = 14),
        legend.text = element_text(size = 12))

LSR

```{r yearly comparisons - plot3}
#| echo: FALSE

# log size ratio
ggplot(d, aes(y2, lsr))+
  geom_hline(aes(yintercept = 0), linetype = 'dashed', linewidth = 1)+
  geom_point(size = 2)+
  geom_line(linewidth = 1)+
  labs(x = 'Year', y = 'log(y2 size/y1 size)')+
  scale_fill_viridis_d(option = 'turbo')+
  scale_color_viridis_d(option = 'turbo')+
  theme_bw()+
  #facet_wrap(~BASIN, nrow = 2)+
  theme(axis.title = element_text(size = 14), 
        axis.text = element_text(size = 14, colour = "gray0"), 
        plot.title = element_text(size = 14, hjust=0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = 'none',
        legend.title = element_text(size = 14),
        strip.text.x = element_text(size = 14),
        legend.text = element_text(size = 12))

@@

```{r - abundance}
#| echo: FALSE
